### 2019-03-21 5_evaluation.tex
Comment.
Add radix figure.
Efficiency plots.
Communication graphs.
More text in evaluation.

The vast majority of systems achieve at or near peak FLOPS. A number
of systems reserve a number of cores (usually 1 or 2) for internal
runtime usage; these systems take a minor hit in peak FLOPS compared
to systems which use all cores for application tasks. Some of the
slower systems struggle to achieve peak FLOPs, though in most cases
the curves suggest that performance would continue to improve if we
were to run larger problem sizes. Unfortunately, the excessive
computational cost of running such tests makes it prohibitively
expensive to run larger problem sizes. For example, the Spark job in
this configuration ran for over 5 hours.

@@

\subsection{Overhead and Scalability}

METG is a useful metric in part because it summarizes the basic task
scheduling overhead of a system in a single number. This makes it
possible to evaluate METG at different node counts to see how it is
impacted by changes in communication topology and latency.

Figure~\ref{fig:metg-compute} shows how METG(50\%) varies with node
count for a variety of dependence patterns supported by Task Bench:

\begin{itemize}
\item Figure~\ref{fig:metg-compute-stencil} is a 1D stencil where each
  task depends on 3 other tasks (including the same point in the
  previous timestep).
\item Figure~\ref{fig:metg-compute-nearest} is a pattern where each
  task depends on its 5 nearest neighbors.
\item Figure~\ref{fig:metg-compute-spread} is a pattern where each
  task depends on 5 distant neighbors, spread as widely as possible
  throughout the machine.
\item Figure~\ref{fig:metg-compute-4x-nearest} shows 4 simultaneous
  copies of the nearest dependence pattern.
\end{itemize}

@@

@@

@@

@@

>>>>

The vast majority of systems achieve at or near peak FLOPS. A number
of systems reserve a number of cores (usually 1 or 2) for internal
runtime usage; these systems take a minor hit in peak FLOPS compared
to systems which use all cores for application tasks. Some of the
slower systems struggle to achieve peak FLOPS, though in most cases
the curves suggest that performance would continue to improve if we
were to run larger problem sizes. Unfortunately, the excessive
computational cost of running such tests makes it prohibitively
expensive to run larger problem sizes. For example, the Spark job in
this configuration ran for over 5 hours.

@@

\subsection{Baseline Overhead}

One of the basic questions when considering different programming
systems is how much overhead the system introduces. This can be a
tricky question to answer directly because some systems introduce
overhead \emph{inline} (i.e., by running system internal processes on
the same cores as application tasks), while other systems introduce
overhead \emph{out-of-line} (i.e., by dedicating one or more cores
solely to runtime use). Some systems, like Charm++, Realm, and Regent,
even support both configurations.

To answer this question, we use the METG metric to determine the
smallest task granularity which can be executed at a given level of
efficiency, as a proxy for overhead. Figure~\ref{fig:metg-compute}
shows how METG(50\%) varies with node count for a variety of
dependence patterns supported by Task Bench:

\begin{itemize}
\item Figure~\ref{fig:metg-compute-stencil} is a 1D stencil where each
  task depends on 3 other tasks (including the same point in the
  previous timestep).
\item Figure~\ref{fig:metg-compute-nearest} is a pattern where each
  task depends 5 others, chosen to be as close as possible.
\item Figure~\ref{fig:metg-compute-spread} is a pattern where each
  task depends on 5 others, spread as widely as possible.
\item Figure~\ref{fig:metg-compute-4x-nearest} shows 4 identical
  copies of the nearest dependence pattern executing concurrently.
\end{itemize}

We observe in the results that the baseline overheads of different
systems can vary by over 5 orders of magnitude. It is worth
remembering when considering this metric that this is a \emph{minimum}
effective task granularity. Therefore applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical average task granularity will
generally be determined by the application domain being
considered. Most notably, for data analytics workloads being run in
industrial data centers, the higher METG values observed for Spark and
TensorFlow are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.

\subsection{Scalability}

METG is a useful metric in part because it summarizes the basic task
scheduling overhead of a system in a single number. This makes it
possible to evaluate METG at different node counts (shown in
Figure~\ref{fig:metg-compute}) to see how it is impacted by changes in
communication topology and latency.

@@

% FIXME: talk about overhead spanning 5 orders of magnitude

@@

\input{e4_radix}

@@

\input{e5_imbalance}

@@

\input{e6_communication}

### 2019-03-21 e3_metg_compute.tex
More text in evaluation.

\subfloat[Stencil.\label{fig:metg-compute-stencil}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_stencil.pdf}
}
\subfloat[Nearest 5 neighbors.\label{fig:metg-compute-nearest}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_nearest.pdf}
}

\subfloat[Spread 5 neighbors.\label{fig:metg-compute-spread}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_spread.pdf}
}
\subfloat[Nearest 5 neighbors, 4 simultaneous task graphs.\label{fig:metg-compute-4x-nearest}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_ngraphs_4_nearest.pdf}
}

\caption{METG vs node count.\label{fig:metg-compute}}
\end{figure*}

>>>>

\subfloat[Stencil pattern.\label{fig:metg-compute-stencil}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_stencil.pdf}
}
\subfloat[Nearest pattern, 5 dependencies per task.\label{fig:metg-compute-nearest}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_nearest.pdf}
}

\subfloat[Spread pattern, 5 dependencies per task.\label{fig:metg-compute-spread}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_spread.pdf}
}
\subfloat[Nearest pattern, 5 dependencies per task, 4 task graphs.\label{fig:metg-compute-4x-nearest}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_ngraphs_4_nearest.pdf}
}

\caption{METG vs node count for different dependence patterns. Lower is better.\label{fig:metg-compute}}
\end{figure*}
